\ttitle

### 2015-08-20 Chapters/Introduction.tex
PrePost SIRS
- All tables and figures
- Tables ending with means have means (sd)
- Included tables have medians (IQR)
- Text includes tables and figures
- Start writing the bloody chapter now!

On the contrary, other authors have reported that obesity is not associated with increased complications after pancreatic surgery. Khan and co-workers reported that while obesity was associated with increased incidence of intra-operative bleeding, there was no increase in complications \parencite{khan_does_2010}. Length of stay in hospital, overall morbidity and in-hospital mortality were not affected by BMI after pancreaticoduodenectomy \parencite{tsai_impact_2010}. while neither BMI nor intra-abdominal visceral fat affected postoperative outcomes in another study of patients undergoing pancreaticoduodenectomy \parencite{balentine_obesity_2011}.

>>>>

On the contrary, other authors have reported that obesity is not associated with increased complications after pancreatic surgery. Khan and co-workers reported that while obesity was associated with increased incidence of intra-operative bleeding, there was no increase in complications \parencite{khan_does_2010}. Length of stay in hospital, overall morbidity and in-hospital mortality were not affected by BMI after pancreaticoduodenectomy \parencite{tsai_impact_2010} while neither BMI nor intra-abdominal visceral fat affected postoperative outcomes in another study of patients undergoing pancreaticoduodenectomy \parencite{balentine_obesity_2011}.
